Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2017-12-21 sections/participants.tex
Added sentence to participants section referring to supplementary materials

%One way to maximize transparency in the selection process is to minimize human decision making steps that introduce biases, and to . 
%We work to achieve this by first assessing the merit of each candidate with respect to the overall goals of the hack week.
%We try to minimize bias in this step by blinding ourselves to a candidate's other attributes, including name and other personal information, and assess their candidacy based soley on questions asked specifically for this purpose.
%When doing this procedure for a large enough sample, it is unlikely that the resulting pool of acceptable candidates is smaller than the number of available spaces at the workshop.

>>>>

We note that participant selection is only the first step in creating a successful hack week. An equal amount of thought and effort should be put into how to facilitate tutorials, break-out sessions and project work such that all participants can successfully and comfortably participate. In the supplementary materials, we give additional suggestions for successful facilitation. 
%One way to maximize transparency in the selection process is to minimize human decision making steps that introduce biases, and to . 
%We work to achieve this by first assessing the merit of each candidate with respect to the overall goals of the hack week.
%We try to minimize bias in this step by blinding ourselves to a candidate's other attributes, including name and other personal information, and assess their candidacy based soley on questions asked specifically for this purpose.
%When doing this procedure for a large enough sample, it is unlikely that the resulting pool of acceptable candidates is smaller than the number of available spaces at the workshop.
